### 2013-12-02 proposal/proposal/Abstract.tex
changes

Web services are loosely-coupled business applications willing to
cooperate in distributed settings within different groups called
communities. Communities aim to provide better visibility,
efficiency, market share and total payoff. There are a number of
proposed mechanisms and models on aggregating web services and
making them cooperate within their communities. However, forming
optimal and stable communities as coalitions to maximize
individual and group efficiency and income has not been addressed
yet. In this paper, we propose an efficient coalition formation
mechanism using cooperative game-theoretic techniques. We propose
a mechanism for community membership requests and selections of
web services in the scenarios where there is interaction between one community and many web services
and scenarios where web services can join multiple established communities. The ultimate objective is to
develop a mechanism for web services to form stable groups
allowing them to maximize their efficiency and generate
near-optimal (welfare-maximizing) communities. The theoretical and
extensive simulation results show that our algorithms provide web services
and community owners, in real-world like environments, with applicable and near-optimal decision
making mechanisms.

>>>>

Web services are loosely-coupled business applications willing to
cooperate in distributed settings within different groups called
communities. Communities aim to provide better visibility,
efficiency, market share and total payoff. There are a number of
proposed mechanisms and models on aggregating web services and
making them cooperate within their communities. However, forming
optimal and stable communities as coalitions to maximize
individual and group efficiency and income for all the involved
parties has not been addressed yet.

In this proposal, we identify the problem of defining efficient
algorithms for coalition formation mechanisms within communities
and propose preliminary results using cooperative game-theoretic
techniques. We propose a mechanism for community membership
requests and selections of web services in the scenarios where
there is interaction between one community and many web services
and scenarios where web services can join multiple established
communities. The ultimate objective is to develop a mechanism for
web services to form stable groups allowing them to maximize their
efficiency and generate near-optimal (welfare-maximizing)
communities. The theoretical and extensive simulation results show
that our algorithms provide web services and community owners, in
real-world like environments, with applicable and near-optimal
decision making mechanisms.

As remaining work in this thesis, we propose to apply different
cooperative game techniques such as nucleus, kernel and bargaining
solution concepts and theoretically analyze those solution
concepts based on functions representing payoff and quality
metrics of the communities. We also aim to apply reinforcement
learning techniques for individual web service strategic decision
making process.

### 2013-12-02 proposal/proposal/chapter1.tex
changes

\setcounter{chapter}{0}
%*******************************START INTRODUCTION **********************************
\chapter{Introduction}\label{sec:intro}
In this chapter we introduce the context of this research, which is about community of web services as autonomous agents and cooperative game theoretic solution concepts. We discuss literature review and their shortcomings then present the motivations behind this work. Also, we discuss our preliminary contributions.

\section{Context}\label{sec:motivation}

@@

@@

In this section, we present a scenario and demonstrate why there is a need for a community of services and why it should satisfy all business models involved.
We first propose an example of a real world scenario, focusing on user experience. Nowadays most of the computer applications are dependent on multiple online service provides, there are a plethora of options available to people in today's society, weather forecasting, ticketing services, map services, local places guides and so on. Most mobile or web applications cannot independently provide this information and they rely on different online services to provide this information.
The high competition within the services industry requires applications to use reliable and high quality online service providers.

If the user were to check a web site or run an application on his/her mobile upon having downtime, or having high response delay or encountering any non-satisfying quality metric, the user will instantly remove the application, which is a huge business concern for application providers. For example, if someone installs a ticketing application on mobile and the application is not using high quality service providers, the user would instantly uninstall the application, which has an extremely negative impact on the visibility of the application. Or let's say you search "Montreal Weather" on a search engine and you click on a web site which is slow because it is using a bad weather web service as source of its raw data, the user will leave the web site and try another link from search results, which has a bad Search Engine Optimization (SEO) effect for the web site, and search engines would not show that web site on search results anymore, which is a business and revenue loss for the application. Thus end user satisfaction is the main goal for online providers otherwise they will lose the market to competitors very quickly. Communities of web service, by providing services with higher quality, higher uptime and reliability for end users, aim to reach this goal. To this end, community management decisions should factor in important QoS parameters while forming the community and during membership management.

High demand on online services has created a big competition on this area. For example an application developer right now needs to choose between hundreds of web services online, providing local places information such as coffees, venues, shops and bars nearby a geographic position. It is hard for new web services to find their customers and be visible for end users amongst hundreds or thousands of other service providers, even if they provide a high quality of service. Hence, community of web services provides them with the chance of joining the communities which already have established market share, and providing them with a great source of revenue, proportional to their QoS and throughput. However, it is important for a community manager to consider all parties involved, for example if market share is not big enough, bringing new web services, can cause revenue drop for the already residing members in community,   since basically there would be not enough tasks and revenue to be shared among web services. This will not affect user satisfaction, but other quality web services may collude, leave, and join another community, hurting the community stability. This is an important issue which has not been addressed previously in similar related works. On the other hand, if communities bound the number of web services exactly to the numbers satisfying their market share, in the case of failure of a web service, the reliability and availability metrics of the community could get hurt. This has also not been efficiently addressed in any other related work. In this research work, we try to propose community formation algorithms, satisfying all parties involved. This is a complete business model, considering end users, community managers and service providers.

\section{Motivation and research Questions}\label{sec:researchquestions}

Web service communities are dynamic by design \cite{DBLP:journals/ijebr/MaamarSTBB09}. In these communities, web services are modeled as intelligent autonomous agents, where they can adopt a strategy maximizing their payoff at any time. A web service has its own right to determine when to join a community and when to leave a community. Community managers can invite or ask a web service to leave in order to maximise their profit. Users can simply stop sending requests to a web service which is not providing satisfactory services. Thus its important to consider all parties involved in community management decision making process. Most of the recent work on communities of services are either
user-centric and focus on user satisfaction
\cite{Chun02user-centricperformance} or system-centric and focus
on the whole system throughput, performance and utilization. There
are many contributions in distributed, grid, cluster and cloud
services which are system-centric. However, in real world
environments and applications, both users and service providers
are self-interested agents, aiming to maximize their own profit.
In those environments, both parties (users and services) will
collaborate as long as they are getting more benefits and payoff.
Our initial research question is:
\emph{How can we model the community of services for the autonomous agents, in order to maximize the throughput for users, web services and community organizers involved?}

In order to address this shortcoming, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed mechanisms to help
users and services to maximize their gain. A two-player
non-cooperative game between web services and community master was
introduced in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}.
In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
for selecting web services has been proposed. In this approach,
the authors proposed a web service selection process that the
community masters can use. The approach considers the efficiency
of all the three involved parties, namely users, web services and
communities. The issue with these solution concepts is that they consider community as whole and model it as one entity in their formulations. A community master decides on behalf of an aggregated function of parameters of all the web services in the community. This can hurt the overall revenue for some individual web services, or even a subset of web services. They can collude and form their own community and gain more, instead of having to adjust and share their resources to other members. Another important issue which needs to be considered is community stability. In community of web services, the web services and community organizers collaborate to perform tasks. Having jointly completed a task and generated revenue, they need to agree on some reasonable method of dividing profits (or tasks) among themselves. This is an key issue for stability of communities which has not had enough attention in related work. If the revenue sharing mechanism is not fair enough for any subset of web services working in the community, as profit maximizing agents, they would just deviate and make their own group inorder to gain more and fair share of profit.
So an important research question that we would like to address is:
\emph{How can we model the the fairness, efficiently in communities of web services and form stable communities?}

@@

In \cite{10.1109/TSC.2012.12}, a cooperative scheme among autonomous
web services based on coalitional game theory has been introduced. They have proposed an algorithm to
reach individually stable coalition partition for web services in order to
maximize their efficiency. The communities choose new web services on the promise
that it would benefit the community without decreasing any other web service's
income. In their model, the worth of community is evaluated with high emphasis on
availability metric and considering price and cost values only. The community structure is based on a coordination chain,
where a web service is assigned as a \emph{primary} web service and the community task distribution
method, will initially invoke the primary web service and only if the primary web service is unavailable
will invoke the next backup web services as they are ordered in the coordination chain. However in cooperative models, it is preferred to
have a real and active cooperative activity engaging all agents to perform the tasks more efficiently. Especially nowadays
with recent advancement in cloud and hardware infrastructures availability is becoming less of an issue. So the backup web services
in their model have a very low chance of getting jobs, especially the ones further in chain, which is huge waste of web services
capabilities.

Another research question we would like to work on is:
\emph{How can we model the community of web services based on cooperative game theory models in a realistic, applicable and practical way?}

@@

\section{Research Objectives and contributions}\label{sec:motexample}

In this research work, I will use game theory to
propose a cooperative game model for the aggregation of web
services within communities. The solution concepts of our
cooperative game seeks to find efficient ways of forming
coalitions (teams) of web services so that they can maximize their
gain and payoff, and distribute the gain in a fair way among all
the web services. Achieving Fairness when the gain is distributed
among the community members is the main factor to keep the
coalition stable as no web service will expect to gain better by
deviating for the community. In other words, the coalition is made
efficient if all the members are satisfied. We first propose a
representation function for communities of web services based on
their QoS attributes. By using this function, we can evaluate the
$worth$ of each community of web services. When facing new
membership requests, a typical community master checks whether the
new coalition having the old and new set of web services will keep
the community stable or not. The community master will reject the
membership requests if it finds out that the new coalition would
be unstable, preventing $any$ subset of web services from gaining
significantly more by deviating from the community and joining
other communities or forming new ones. The computation of
solutions for cooperative game theory problems is combinatorial in
nature and proven to be NP-complete \cite{Algorithmic}, making
this computation impractical in real world applications. However,
using the concepts of coalition stability, we propose
approximation algorithms running in polynomial time providing web
services and community masters with applicable and near-optimal
decision making mechanisms.

\indent In this proposal, I will address the problem of forming stable and efficient coalitions for maximising web services and community revenue.
The main objectives in this proposal work are:
\begin{itemize}
\item To apply cooperative game theory solution concepts in order to address the problem of optimizing coalition formation for a stable community that can maximise the total payoff.
\item To reduce the complexity of cooperative game theory solution concepts tailored to the problem model of communities of web services in order to make these solutions applicable in real world scenarios.
\item To increase community stability by subsiding and taxation methods.
\item To validate the proposed methods by simulation and comparing our results with other similar works.
\end{itemize}

\section{Proposal Organization}\label{sec:outline}
The rest of the proposal is organized as follows: We present in Chapter~\ref{sec:MAS} the background
needed for our research along with the relevant related work. Chapter~\ref{sec:coalitionformationws} provides the problem statement and presents our solution model in two
different scenarios with some primitive results. Finally in Chapter~\ref{sec:conclusionfuturework}, we present our conclusion, future plan, and the timetable of our research.

>>>>

\setcounter{chapter}{0}
%*******************************START INTRODUCTION **********************************
\chapter{Introduction}\label{sec:intro}
In this chapter, we introduce the context of this research, which
is about communities of web services abstracted as autonomous
agents. Those agent-based web services use cooperative game
theoretic solution concepts for decision making. We discuss the
motivations of this work and briefly review the literature to
identify the problems we aim to solve in this thesis. Moreover, we
discuss our objectives and preliminary contributions.

\section{Context of Research}\label{sec:motivation}

@@

Typically, web services are business applications deployed as
autonomous and interoperable agents \cite{Alescio}. In fact, the
W3C consortium defines a web service as ``an abstract notion that
must be implemented by a concrete agent''. However, the web is
stocked with agent-based services that offer similar business
functionalities, which leads to service consumers having
difficulties in choosing the most appropriate agents to interact
with.

@@

In this section, we present a scenario and demonstrate why there
is need for communities of services. We first propose an example
of a real world scenario, focusing on user experience. There are a
plethora of options available to people in today's society,
including weather forecasting, ticketing services, map services,
local places guides and so on. Most mobile or web applications
cannot independently satisfy users requests and should rely on
different online services. The high competition within the
services industry requires applications to use reliable and high
quality online service providers.

If the user were to check a web site or run an application on her
mobile device upon having downtime, or having high response delay
or encountering any non-satisfying quality metric, she will
instantly remove the application, which is a huge business concern
for application providers. For example, if a user installs a
ticketing application on her mobile device and the application is
not using high quality service providers, the user would instantly
uninstall the application, which has an extremely negative impact
on the
visibility of the application. %Let us say you search "Montreal
%Weather" on a search engine and you click on a web site which is
%slow because it is using a bad weather web service as source of
%its raw data, the user will leave the web site and try another
%link from search results, which has a bad Search Engine
%Optimization (SEO) effect for the web site, and search engines
%would not show that web site on search results anymore, which is a
%business and revenue loss for the application.
Thus, end user satisfaction is the main goal for competitive
online providers. Communities of web service, by providing
services with higher quality, higher uptime and reliability for
end users, aim to reach this goal. To this end, community
management decisions should capitalize on important QoS parameters
while forming the community and during membership management.

High demand on online services has created a massive business
competition. For example, nowadays users are provided with
multiple choices of web services offering local places information
such as coffees, venues, and shops nearby a geographic position.
It is hard for new web services to find their customers and be
visible for end users amongst hundreds or thousands of other
available services, even if they provide a high quality of
service. Hence, the concept of communities of web services
provides them with the chance of joining a platform with an
established market share and reputation. However, it is crucial
for a community manager to consider many factors when inviting or
accepting new members. For example, if the market share is not big
enough, bringing new web services can cause revenue drop for the
already residing members. This may encourage other web services to
collude, leave, or join other communities, hurting the community
stability. This is an important issue which has not been addressed
previously in the relevant literature. On the other hand, if
communities bound the number of web services to ensure higher
revenue, availability and response time could be negatively
affected if some members encounter problems. This is because
alternative web services for substitution will be limited.  This
has also not been efficiently addressed in the related work.
Consequently, community formation algorithms satisfying some
desirable properties such as community stability and overall
revenue are yet to be defined considering end users, community
managers and service providers.

\section{Motivation and Research Questions}\label{sec:researchquestions}

Web service communities are dynamic by design
\cite{DBLP:journals/ijebr/MaamarSTBB09}. In these communities, web
services are modeled as intelligent autonomous agents, where they
can adopt a strategy maximizing their payoff at any time. A web
service can ask joining a community and has the right to leave it.
Community managers can invite or ask a web service to leave in
order to maximize the community profit. Users can simply stop
sending requests to a web service which is not providing
satisfactory services. Thus its important to consider all the
parties involved in the decision making process about the
community management. Most of the recent work on communities of
services are either user-centric and focus on user satisfaction
\cite{Chun02user-centricperformance} or system-centric and focus
on the whole system throughput, performance and utilization. There
are many contributions in distributed, grid, cluster and cloud
services which are system-centric. However, in real world
environments and applications, both users and service providers
are self-interested agents, aiming to maximize their own profit.
In those environments, both parties (users and services) will
collaborate as long as they are getting more benefits and payoff.
Our initial research question is: \emph{How can we model the
community of agent-based services in order to maximize the utility
of involved users, web services and community organizers?}

In order to address this problem, recently
\cite{DBLP:conf/IEEEscc/LimTMB12,
DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed
mechanisms to help users and services maximize their gain. A
two-player non-cooperative game between web services and community
master was introduced in
\cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In
\cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
for selecting web services has been proposed. In this approach,
the authors proposed a web service selection process that the
community masters can use. The approach considers the efficiency
of all the three involved parties, namely users, web services and
communities. The issue with these solution concepts is that they
consider community as a whole and model it as one entity in their
formulations. A community master decides on behalf of all the
members using an aggregated function of parameters. This can hurt
the overall revenue for some individual web services, or even a
subset of web services. Those services can collude and form their
own community and gain more, instead of having to adjust and share
their resources with other members. Another important issue which
needs to be considered is the community stability. In community of
web services, the members and community organizers collaborate to
perform tasks. Having jointly completed a task and generated
revenue, they need to agree on some reasonable method of dividing
profits (or tasks) among themselves. This is a key issue for the
group stability still to be investigated. If the revenue sharing
mechanism is not fair enough for any subset of web services
working in the community, these agents, as profit maximizing
entities, would just deviate and make their own group. So an
important research question that we would like to address is:
\emph{How can we model fair and stable communities as coalitions
of agent-based web services?}

@@

In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
autonomous web services based on coalitional game theory has been
introduced. The authors have proposed an algorithm to reach
individually stable coalition partition for web services in order
to maximize their efficiency. The communities choose new web
services on the promise that it would benefit the community
without decreasing any other web service's income. In their model,
the worth of community is evaluated with high emphasis on the
availability metric and considering price and cost values only.
The community structure is based on a coordination chain, where a
web service is assigned as a \emph{primary} web service and the
community task distribution method will initially invoke the
primary web service. Only if the primary web service is
unavailable, the next backup web services in the ordered
coordination chain will be invoked. However, in cooperative
models, it is preferred to have a real and active cooperative
activity engaging all agents to perform the tasks more
efficiently. Thus, the final research question we would like to
work on is: \emph{How can we model and analyze the cooperation
among the community members in realistic, applicable and practical
settings?}

@@

\section{Research Objectives and Contributions}\label{sec:motexample}

In this research work, our first objective is to propose a
cooperative model as game for the aggregation of web services
within communities. The solution concepts of our cooperative game
seeks to find efficient ways of forming coalitions (teams) of web
services so that they can maximize their gain and payoff, and
distribute the gain in a fair way among all the member services.
Achieving Fairness when the gain is distributed among the
community members is the main factor to keep the coalition stable
as no web service will expect to gain better by deviating from the
community. In other words, the coalition is made efficient if all
the members are satisfied. We first propose a representation
function for communities of web services based on their QoS
attributes. By using this function, we can evaluate the $worth$ of
each community of web services. When facing new membership
requests, a typical community master checks whether the new
coalition having the old and new set of web services will keep the
community stable or not. The community master will reject the
membership requests if it finds out that the new coalition would
be unstable, preventing $any$ subset of web services from gaining
significantly more by deviating from the community and joining
other communities or forming new ones. The computation of
solutions for cooperative games is combinatorial in nature and
proven to be NP-complete \cite{Algorithmic}, making this
computation impractical in real world applications. However, using
the concepts of coalition stability, the second objective is to
investigate approximation algorithms running in polynomial time
providing web services and community masters with applicable and
near-optimal decision making mechanisms.

\indent To summarize, the main problem we aim to tackle in this
thesis is the formation of stable and efficient coalitions
maximizing web services and community revenue. The main objectives
are:
\begin{itemize}
\item To propose a cooperative model and analyze its solution
concepts in order to address the problem of optimizing coalition
formation for a stable community.

\item To reduce the complexity of computing the solution concepts
of the cooperative model tailored to the problem of communities of
agent-based web services in order to make these solutions
applicable in real world scenarios.

\item To analyze the effect of different membership and taxation
models that the master can apply to the members on the stability
of the community.

\item To investigate the impact of learning on individual and
group decision making within the cooperative model of the
community.

\item To validate the proposed methods by extensive simulations
and comparison with other similar proposals.
\end{itemize}

\section{Proposal Organization}\label{sec:outline}
The rest of the proposal is organized as follows: We present in
Chapter~\ref{sec:MAS} the background needed for our research along
with relevant related work. Chapter~\ref{sec:coalitionformationws}
provides the problem statement and presents our solution model in
two different scenarios with some preliminary results. Finally, in
Chapter~\ref{sec:conclusionfuturework}, we present our conclusion,
future plan, and the timetable of our research.

### 2013-12-02 proposal/proposal/chapter2.tex
changes

In this chapter, we briefly review web services, then we introduce the concept of communities of web services, their architecture and applications and the benefits of forming communities. Then we discuss the cooperative game theory concepts used throughout our research work. Finally, we discuss the relevant related work on web service communities and games in service oriented computing literature.

    \section{Community of Web Services}\label{sec:CommunityWS}
        In this section, we discuss the concept of communities of web services, and we discuss the architecture and operations of community members.

>>>>

In this chapter, we briefly review web services, then we introduce
the concept of communities of web services, their architecture and
applications and the benefits of forming communities. Thereafter,
we discuss the cooperative game theory concepts used throughout
the proposal. Finally, we discuss relevant related work on web
service communities and games in the literature of service
oriented computing.

    \section{Community of Web Services}\label{sec:CommunityWS}
    In this section, we present web services and discuss the concept
    of their communities from architectural and operations
    perspectives.
